paper

### 2024-09-18 paper.qmd
paperwork

# Set metadata and formula for LimROTS analysis
meta.info <- "mixing.ratio"
B <- 1000  # Number of bootstrap samples
K <- dim(BM21.Case0)[1]/4  # Set the value for K based on the data size
K <- floor(K) 
num_cores <- 30   # Number of cores for parallel processing
cluster <- makeCluster(num_cores)  # Create a parallel cluster
group.name <- "mixing.ratio"
formula.str <- "~ 0 + mixing.ratio"  # Formula for group comparison

# Run LimROTS analysis with trend and robust settings enabled
limrots.result <- LimROTS(data.exp = BM21.Case0, 
                          B = B, K = K, meta.info = meta.info, 
                          cluster = cluster, group.name = group.name, 
                          formula.str = formula.str, trend = TRUE, robust = TRUE)
```

@@

#trace(LimROTS , edit = T)
# Run LimROTS analysis with trend and robust settings enabled
rots.result <- LimROTS(data.exp = BM21.Case0, 
                          B = B, K = K, meta.info = meta.info, 
                          cluster = cluster, group.name = group.name, 
                          formula.str = formula.str, trend = TRUE, robust = TRUE, n.ROTS = T)
```

@@

saveRDS(limma.result, "../LimROTS paper/BM21.case0.limma.rds")
```

@@

# Load the dataset
load("../LimROTS paper/metabolomics/BM21.Case1.rda")

@@

length(which(limrots.result.df$q.value < 0.05))
length(which(limrots.result.df$fdr < 0.05))

limrots.result.df <- limrots.result.df[limrots.result.df$q.value < 0.05,]

length(which(grepl("_pluseffect", row.names(limrots.result.df)) ))

length(which(grepl("synthetic", row.names(limrots.result.df)) ))
```

>>>>

# Set metadata and formula for LimROTS analysis
meta.info <- "mixing.ratio"
B <- 1000  # Number of bootstrap samples
K <- dim(BM21.Case0)[1]/4  # Set the value for K based on the data size
K <- floor(K) 
num_cores <- 10   # Number of cores for parallel processing
cluster <- makeCluster(num_cores)  # Create a parallel cluster
group.name <- "mixing.ratio"
formula.str <- "~ 0 + mixing.ratio"  # Formula for group comparison

# Run LimROTS analysis with trend and robust settings enabled
limrots.result <- LimROTS(data.exp = BM21.Case0, 
                          B = B, K = K, meta.info = meta.info, 
                          cluster = cluster, group.name = group.name, 
                          formula.str = formula.str, trend = TRUE, robust = TRUE)

saveRDS(limrots.result , "paperdata/BM21.Case0.limrots.rds")
```

@@

#trace(LimROTS , edit = T)
# Run LimROTS analysis with trend and robust settings enabled
rots.result <- LimROTS(data.exp = BM21.Case0, 
                          B = B, K = K, meta.info = meta.info, 
                          cluster = cluster, group.name = group.name, 
                          formula.str = formula.str, trend = TRUE, robust = TRUE, n.ROTS = T)

saveRDS(rots.result , "paperdata/BM21.Case0.rots.rds")
```

@@

saveRDS(limma.result , "paperdata/BM21.Case0.limma.rds")
```

limrots.result <- readRDS("paperdata/BM21.Case0.limrots.rds")
rots.result <- readRDS("paperdata/BM21.Case0.rots.rds")
limma.result <- readRDS("paperdata/BM21.Case0.limma.rds")

alpha_thresholds <- seq(0, 0.075, by = 0.01)
significant_limROTS <- sapply(alpha_thresholds, function(alpha) sum(limrots.result$q_values$qvalues < alpha))
significant_ROTS <- sapply(alpha_thresholds, function(alpha) sum(rots.result$FDR < alpha))
significant_limma <- sapply(alpha_thresholds, function(alpha) sum(limma.result$adj.P.Val < alpha))

plot_data <- data.frame(Alpha = alpha_thresholds, significant_limROTS = significant_limROTS,
                        significant_ROTS = significant_ROTS , significant_limma = significant_limma )

@@

# Load the dataset
data(BM21.Case1)

@@
